\bibliographystyle{plain}
\begin{thebibliography}{9}

\bibitem{Andreas Anyuru}
  Andreas Anyuru,
  \emph{Professional WebGL Programming: Developing 3D Graphics for the Web},
  John Wiley and Sons Ltd, West Sussex,
  2012.
  
\bibitem{Can I Use}
  Alexis Deveria,
  \emph{Can I use" provides up-to-date browser support tables for support of front-end web technologies on desktop and mobile web browsers.},
  \url{caniuse.com}
  
\bibitem{OpenGL Website}
	\emph{This is the official OpenGL Website, where they've stated a lot of information on the history of OpenGL},
	\url{https://www.opengl.org/about/}
	
\bibitem{Heterogeneous Computing Techniques}
	Sparsh Mittal and Jeffrey S. Vetter
	\emph{A Survey of CPU-GPU Heterogeneous Computing Techniques},
	Oak Ridge National Laboratory and Georgia Tech,
	2015.
	
\bibitem{Bugaboo}
	Bugaboo
	\emph{Bugaboo configurator},
	Bugaboo website,
	Oct. 2015.
	\url{http://blog.irayrender.com/post/112595883086/bugaboo-configurator-making-of}
	
\bibitem{iRayBlog}
	3Dimerce
	\emph{Bugaboo configurator Making of},
	iRender blog,
	Oct. 2015.
	\url{https://www.bugaboo.com/NL/nl_NL/strollers/create?sId=CAM3STD}
	
\bibitem{latency}
	Wikipedia
	\emph{HTTP/2},
	Oct. 2015.
	\url{https://en.wikipedia.org/wiki/HTTP/2#Differences_from_HTTP_1.1}
	
\bibitem{Ajax: A New Approach to Web Applications}
	Jesse James Garrett
	\emph{Ajax: A New Approach to Web Applications},
	Feb. 2005.
	\url{https://courses.cs.washington.edu/courses/cse490h/07sp/readings/ajax_adaptive_path.pdf}
	
\bibitem{Agile: User Stories}
	Scott W. Ambler
	\emph{2. Initial User Stories (Formal)}
	2003 - 2014
	\url{http://www.agilemodeling.com/artifacts/userStory.htm}
	
\bibitem{Agile: Technical Requirements}
	Scott W. Ambler
	\emph{Figure 1. Technical requirements (summary form).}
	2003 - 2014
	\url{http://agilemodeling.com/artifacts/technicalRequirement.htm}
	
\bibitem{Response Times}
	Jakob Nielsen
	\emph{Response Times: The 3 Important Limits}
	January, 1993
	\url{https://www.nngroup.com/articles/response-times-3-important-limits/}
	
\bibitem{User Experience}
	Don Norman \& Jakob Nielsen
	\emph{The Definition of User Experience}
	July, 2016
	\url{https://www.nngroup.com/articles/definition-user-experience/}
	
\bibitem{Back-End Developer Definition}
	Techopedia
	\emph{Back-End Developer}
	\url{https://www.techopedia.com/definition/29568/back-end-developer}
	
\bibitem{Back-End Developer Definition 02}
	Bloc
	\emph{A Comparison of Frontend and Backend Web Development}
	Dec. 2016
	\url{https://blog.bloc.io/frontend-vs-backend-web-development/}
	
\bibitem{Dollar Shave Club back-end}
	High Scalability
	\emph{The Dollar Shave Club Architecture Unilever Bought For \$1 Billion}
	Sep. 2016
	\url{http://highscalability.com/blog/2016/9/13/the-dollar-shave-club-architecture-unilever-bought-for-1-bil.html}
	
\bibitem{Uber back-end}
		High Scalability
	\emph{How Uber Manages A Million Writes Per Second Using Mesos And Cassandra Across Multiple Datacenters}
	Sep. 2016
	\url{http://highscalability.com/blog/2016/9/28/how-uber-manages-a-million-writes-per-second-using-mesos-and.html}
	
\bibitem{Microservices}
	microservices.io
	\emph{Pattern: Microservices Architecture}
	Dec. 2016
	\url{http://microservices.io/patterns/microservices.html}
	
\bibitem{Elixr}
	Elixer Programming Language
	\emph{Elixer Programming Language}
	\url{http://elixir-lang.org/}
	
\bibitem{Firebase}
	Firebase
	\emph{Firebase}
	\url{https://firebase.google.com/}
	
\end{thebibliography}